---
title: "Random Grid"
subtitle: "Figs"
author: "L Kell & A Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, knitr, eval=TRUE, echo=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment   =NA, 
               warning   =FALSE, 
               message   =FALSE, 
               error     =FALSE, 
               echo      =FALSE,
               fig.width =10, 
               fig.height=10,
               cache     =TRUE, 
               fig.path  ="../tex/rg-",
               cache.path="../cache/rg/")

iFig=0
iTab=0
```
```{r, dir}
dirMy=dirname(dirname(FLife:::getScriptPath()))
dirMy="/home/laurence/Desktop/sea++/mydas/tasks/task4"
dirDat="/home/laurence/Desktop/Dropbox/mydasOMs/data"
dirRes="/home/laurence/Desktop/Dropbox/mydasOMs/results"
dirTex="/home/laurence/Desktop/sea++/mydas/project/papers/randomGrid/tex"
```
```{r, pkgs}
library(ggplot2)
library(plyr)
library(dplyr)
library(reshape)
library(GGally)

library(FLCore)
library(FLBRP)
library(FLasher)
library(ggplotFL)
library(FLife)

library(wesanderson)
```

## Life history parameters

```{r, priors}
vonBFn=function(age,params){
  
  dimnames(params)[[1]]=tolower(dimnames(params)[[1]])
  
  res=params["linf"]%*%(1.0-exp((-params["k"])%*%(age%-%params["t0"])))
  
  dimnames(res)=dimnames(age)
  res}

load(file.path(dirDat,"brill.RData"))
prior=rbind(prior[-4],vonBFn(prior,age=prior["a50"]))
pr=cbind(spp="brill",model.frame(prior))

load(file.path(dirDat,"turbot.RData"))
prior=rbind(prior[-4],vonBFn(prior,age=prior["a50"]))
pr=rbind.fill(pr,cbind(spp="turbot",model.frame(prior)))

load(file.path(dirDat,"ray.RData"))
prior=rbind(prior[-4],vonBFn(prior,age=prior["a50"]))
pr=rbind.fill(pr,cbind(spp="ray",model.frame(prior)))

load(file.path(dirDat,"pollack.RData"))
prior=rbind(prior[-4],vonBFn(prior,age=prior["a50"]))
pr=rbind.fill(pr,cbind(spp="pollack",model.frame(prior)))

load(file.path(dirDat,"sprat.RData"))
prior=rbind(prior[-4],vonBFn(prior,age=prior["a50"]))
pr=rbind.fill(pr,cbind(spp="sprat",model.frame(prior)))
names(pr)[22]="l50"

params=pr
rm(pr)  

k=ddply(params,.(spp), with, mean(k))
ord=ac(k[order(k$V1),"spp"])
params$spp=factor(params$spp,levels=ord)
#save(params,file="/home/laurence/Desktop/sea++/mydas/project/papers/randomGrid/data/params.RData")
```


```{r, lhpar, fig.height=3}
ggplot(transform(melt(params[,c("spp","linf","k","l50")]),  
                 variable=factor(variable,level=c("k","linf","l50"))))+
        geom_boxplot(aes(x = spp, y = value),size = 0.5, notch = FALSE,fill="grey",outlier.shape = 20, fatten=0.5)          +
        theme_bw() +
        theme(plot.title = element_text(size = 14,face = "bold"),
              text = element_text(size = 14),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 14, angle = 45, hjust = 1),
              panel.grid.major=element_blank(),
              panel.grid.minor=element_blank(),
              strip.background=element_blank()
              ) +
        facet_wrap( ~ variable, scale="free")+expand_limits(y=0)+ylab("")+xlab("")

ggsave(filename=file.path(dirTex,"fig1.png"), last_plot(),dpi=300, units='in',width=6, height=3)
```

**Figure `r iFig=iFig+1; iFig`** Life history parameters.


```{r, derived, fig.height=8}
ggplot(transform(melt(params[,c("spp","spr0","lopt","r","rc","fm","mk","bmsy","fmsy","msy")]),
                 variable=factor(variable,
                          level=c("r","rc","spr0","lopt","fm","mk","bmsy","fmsy","msy"))))+
  geom_boxplot(aes(x = spp, y = value),size = 0.5, notch = FALSE,         fill="grey",outlier.shape = 20, fatten=0.5) +
        theme_bw() +
        theme(plot.title = element_text(size = 14,face = "bold"),
              text = element_text(size = 14),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 14, angle = 45, hjust = 1),
              panel.grid.major=element_blank(),
              panel.grid.minor=element_blank(),
              strip.background=element_blank()
              ) +
        facet_wrap( ~ variable, scale="free")+expand_limits(y=0)+ylab("")+xlab("")
  
ggsave(filename=file.path(dirTex,"fig2.png"), last_plot(),dpi=300, units='in',width=10, height=8)
```

**Figure `r iFig=iFig+1; iFig`** Reference points.


## Equilibrium dynamics

The parameters are then used by `lhEql` to simulate the equilibrium dynamics by combining the spawner/yield per recruit relationships with a stock recruiment relationship.

```{r, eqRun}
eq=lhEql(lh,spwn=0)
```


```{r vectors}
sel<-function(x) 
  catch.sel(x)%/%fapex(catch.sel(x))

len<-function(x)
  (stock.wt(x)%^%(1/lh["b"]))

load(file.path(dirDat,"brill.RData"))
dat=FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Length"=len)
vct=cbind(spp="brill",as.data.frame(FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Length"=len)))

load(file.path(dirDat,"turbot.RData"))
dat=FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Length"=len)
dat=cbind(spp="turbot",as.data.frame(FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Length"=len)))
vct=rbind(vct,dat)

load(file.path(dirDat,"ray.RData"))
dat=FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Length"=len)
dat=cbind(spp="ray",as.data.frame(FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Length"=len)))
vct=rbind(vct,dat)

load(file.path(dirDat,"pollack.RData"))
dat=FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Length"=len)
dat=cbind(spp="pollack",as.data.frame(FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Length"=len)))
vct=rbind(vct,dat)

load(file.path(dirDat,"sprat.RData"))
dat=cbind(spp="sprat",as.data.frame(FLQuants(eq,"M"=m,"Selectivity"=sel,"Maturity"=mat,"Length"=len)))
vct=rbind(vct,dat)

vct=ddply(vct,.(spp,age,qname),with, quantile(data))
     
ggplot(subset(vct,age<=10))+
  geom_ribbon(aes(age,ymax=`75%`,ymin=`25%`,col=spp,fill=spp),alpha=0.7)+
  geom_line(aes(age,`50%`,col=spp))+
  facet_wrap(~qname,scale="free")+
  scale_x_continuous(limits=c(0,10))+
  xlab("Age")+ylab("")+ theme_bw() +
        theme(plot.title = element_text(size = 14,face = "bold"),
              text = element_text(size = 14),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 14, hjust = 1),
              panel.grid.major=element_blank(),
              panel.grid.minor=element_blank(),
              strip.background=element_blank()
              )+
    scale_color_brewer(palette = "Greys")+
    scale_fill_brewer(palette = "Greys")+
  theme(legend.position="bottom")
ggsave(filename=file.path(dirTex,"fig3.png"), last_plot(),dpi=300, units='in',width=8, height=8)
```

**Figure `r iFig=iFig+1; iFig`** Vectors.


```{r, eq}
load(file.path(dirDat,"turbot.RData"))

plot(iter(eq,1),refpts=FALSE) + theme_bw()+theme(plot.title = element_text(size = 14,face = "bold"),
              text = element_text(size = 14),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 14, hjust = 1),
              panel.grid.major=element_blank(),
              panel.grid.minor=element_blank(),
              strip.background=element_blank()
              )  
ggsave(filename=file.path(dirTex,"figeq_notin_paper.png"), last_plot(),dpi=300, units='in',width=8, height=6)
```

**Figure `r iFig=iFig+1; iFig`** Equilibrum Curves.

## Population dynamics

```{r ts}
load(file.path(dirDat,"turbot.RData"))

dat=FLQuants(window(om,start=10,end=60), 
          "ssb" = function(x) ssb(x)%/%refpts( eq)["msy","ssb"], 
          "f" =   function(x) fbar(x)%/%refpts(eq)["msy","harvest"], 
          "rec" = function(x) rec(x)%/%refpts( eq)["msy","rec"], 
          "catch"=function(x) landings(x)%/%refpts(eq)["msy","yield"])
plot(dat, fill="grey50")+ theme_bw()+theme(plot.title = element_text(size = 14,face = "bold"),
              text = element_text(size = 14),
              axis.title = element_text(face="bold"),
              axis.text.x=element_text(size = 14, hjust = 1),
              panel.grid.major=element_blank(),
              panel.grid.minor=element_blank(),
              strip.background=element_blank()
              ) 
ggsave(filename=file.path(dirTex,"fig4.png"), last_plot(),dpi=300, units='in',width=6, height=6)
```

**Figure `r iFig=iFig+1; iFig`** Time series relative to MSY benchmarks.

# Results

```{r}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/pm.RData")
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/smry.RData")
```

```{r, smry-plot, fig.height=8,fig.width=12}
ggplot(ddply(smry,.(spp,year,qname,.id), with, quantile(data,na.rm=TRUE)))+
  geom_ribbon(aes(year,ymin=`25%`,ymax=`75%`,fill=.id),alpha=0.2)+
  geom_path(aes(year,`50%`,col=.id))+
  facet_grid(qname~spp,scale="free")+
  theme(legend.position="bottom")
```

```{r, smry-plot-2, fig.height=8,fig.width=12}
ggplot(ddply(smry,.(spp,year,qname,.id), with, quantile(data,na.rm=TRUE)))+
  geom_ribbon(aes(year,ymin=`25%`,ymax=`75%`,fill=.id),alpha=0.2)+
# geom_path(aes(year,`50%`,col=.id))+
  geom_path(aes(year,data,col=.id,group=paste(iter,.id,spp,qname)),linetype="23",data=subset(smry,iter%in%c(12)))+
  facet_grid(qname~spp,scale="free")+
  theme(legend.position="bottom")
```

```{r}
load("/home/laurence/Desktop/Dropbox/mydasOMs/results/pm.RData")

minMax<-function(x,na.rm=TRUE) (x-min(x,na.rm=na.rm))/diff(range(x,na.rm=na.rm))
mseStart=c("brill"=54,"turbot"=54,"ray"=60,"pollack"=56,"sprat"=52,"razor"=54,"lobster"=57)

scen=expand.grid(spp    =c("brill",   "turbot",   "ray",   "pollack",   "sprat"),
                 control=1:12,
                 stringsAsFactors=FALSE)

dt=transform(pm,k1=cut(k1,breaks=seq(0,1,0.1)),
                k2=cut(k2,breaks=seq(0,1,0.1)))

dt2=ddply(dt,.(spp,k1,k2), with, 
                   data.frame(kobe  =mean(kobe.n),
                              safety=mean(safety),
                              yield =mean(yield),
                              aav   =(mean(1-yieldAav))))
dt3=melt(dt2,id=c("k1","k2","spp"))
dt4=ddply(dt3,.(variable,spp), transform, value=minMax(value))

dt4$spp  =factor(dt4$spp,     level=c("ray","pollack","turbot","brill","sprat"))
dt4$qname=factor(dt4$variable,level=c("safety","kobe","yield","aav"))
```

```{r, grid}
library(dplyr)  

mycol=rev(c("navy","blue","cyan","lightcyan","yellow","red","red4"))
ggplot(dt4)+
  geom_tile(aes(k1,k2,fill=value))+
  scale_fill_gradientn(colours=mycol)+
  facet_grid(spp~variable)

dt2=ddply(dt,.(spp,k1,k2), transmute, 
                   u1 =mean(kobe.n)/45,
                   u2 =mean(yield),
                   u3 =mean(safety),
                   u4 =mean(kobe.n)+mean(yield)+mean(safety)+mean(1-yieldAav))

dt2=transform(dt2,u2=u1*u2,u3=u1*u2*u3,u4=u1*u2*u3*u4)
dt3=melt(dt2,id=c("k1","k2","spp"))
dt4=ddply(dt3,.(variable,spp), transform, value=minMax(value))

dt4$spp  =factor(dt4$spp,     level=c("ray","pollack","turbot","brill","sprat"))
dt4$qname=factor(dt4$variable,level=c("safety","kobe","yield","aav"))
```

```{r, grid-2}
ggplot(aes(as.numeric(k1),as.numeric(k2),z=value),data=dt4)+  
  geom_tile(aes(k1,k2,fill=value))+
  scale_fill_gradientn(colours=mycol)+
  facet_grid(spp~variable)
```

```{r}
library(akima)

t=ddply(pm,.(spp), with, {
  t=interp(k1,k2,z=yield,xo=seq(0,1,.05),yo=seq(0,1,.02),duplicate="mean")
  cbind(expand.grid(x=t$x,y=t$y),z=c(t$z))})

ggplot(aes(x,y,z=z),data=t)+
  geom_tile(aes(x,y,fill=z))+
  scale_fill_gradientn(colours=mycol)+
#stat_contour(aes(colour= ..level..),breaks=seq(0,1,.1))+
  facet_wrap(~spp,ncol=2)
```


\newpage
## Software Versions

* `r version$version.string`
* FLCore:    `r packageVersion('FLCore')`
* FLBRP:     `r packageVersion('FLBRP')`
* FLasher:   `r packageVersion('FLasher')`
* FLife:     `r packageVersion('FLife')`
* ggplotFL:  `r packageVersion('ggplotFL')`
* **Compiled**: `r date()`

## Author information

**Laurence Kell**. laurie@seaplusplus.es

## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.

# References {#References}

\newpage
# Session Info

```{r}
sessionInfo()
```

