---
title: "Random Grid Results"
author: "Alex Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---


```{r, libs}
library(plyr)
library(dplyr)
library(reshape)
library(broom)
library(ggpubr)
library(ggpmisc)
library(mgcv)
library(RColorBrewer)
library(RPostgreSQL)

```


```{r, data}
drv =dbDriver("PostgreSQL")
#laurie db
con=dbConnect(drv,
              host ='wklife.csrzweaa3tbm.eu-west-2.rds.amazonaws.com',
              dbname  ='wklife',
              port    =5432,
              user    ='mydas',
              password='Yes_Meski')

empd_pm=dbGetQuery(con, "select * from randgridpm")
```

```{r,blockimage,echo=TRUE,eval=TRUE}
empd_pm$kobe.p=empd_pm$kobe.n/45
empd_pm$yieldAav = pmin(0.5,empd_pm$yieldAav)
empd_pm$yieldAav = 1 - empd_pm$yieldAav
test=melt(empd_pm, id.vars=c("spp","k1","k2","iter","j"),measure.vars=c("safety","kobe.p","yield","yieldAav"))[,c("spp","k1","k2","iter","value","variable")]
```

## modelled display using GAM
```{r, modelloop, echo=TRUE,eval=TRUE}
pairwise = list()
for (i in c("safety","kobe.p","yield","yieldAav")){
<<<<<<< HEAD
  for (j in c("brill","turbot","ray","pollack","sprat")){
    a    = subset(test, spp==j & variable %in% c(i))
    spl1 <- gam(value ~ s(k1, k2, bs = 'sos'), data = a)
=======
  for (j in c("brill","turbot","ray","pollack","sprat")[4]){
    a    = subset(test, spp==j & variable==i)[,c("k1","k2","value")]
    spl1 = gam(value ~ s(k1, k2, bs = 'sos'), data = a)
>>>>>>> 020de6f14437757d6d9ad779412cbb3950a9c7da
    # fine grid, coarser is faster
    datmat2 <- data.frame(expand.grid(k1 = seq(0, 1, 0.01), k2= seq(0, 1, 0.01)))
    resp <- predict(spl1, datmat2, type = "response")
    datmat2$value <- resp
    datmat2$spp = j
    datmat2$objective = i
    pairwise=rbind(pairwise, datmat2)
  }
}  
```
```{r, pairwiseplots, echo=TRUE, fig=TRUE}
minMax=function(x,na.rm=TRUE) (x-min(x,na.rm=na.rm))/diff(range(x,na.rm=na.rm))
pairwise2=ddply(pairwise,.(spp,objective),transform, var2=minMax(value))

pairwise2$spp = factor(pairwise2$spp, levels=c("ray","pollack","turbot","brill", "sprat"))
mycol = rev(c("navy", "blue", "deepskyblue1", "deepskyblue", "yellow", "darkorange", "darkorange4"))
pairwise2=pairwise2[!is.na(pairwise2$spp), ]
ggplot(pairwise2) + 
  aes(x = k1, y = k2, z = var2, fill = var2) + 
  geom_tile() + 
  #coord_equal() +
  #geom_contour(color = "white", alpha = 0.5) + 
  #scale_fill_distiller("",palette="Spectral", na.value="white", direction=1) + 
  #geom_contour(color = "white", alpha = 0.1) + 
  scale_fill_gradientn("PM",colours=mycol, breaks=c(0, 0.5, 1))+
  geom_contour(color = "white", alpha = 0.3) + 
  #scale_fill_distiller("",palette="Spectral", na.value="white", direction=1, breaks=c(0, 0.5, 1))+
  theme_bw()+facet_grid(spp~objective) +
  theme(text = element_text(size=18, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        legend.position="bottom",panel.spacing = unit(1, "lines")
  ) + ylab("k2")+xlab("k1")
```
## utilities
```{r, utilities, echo=TRUE,eval=TRUE}

pair=reshape( pairwise, idvar = c("spp","k1","k2"), v.names = "value", timevar = "objective", 
              direction = "wide") 
colnames(pair)[4:7] = c("safety","kobe.p","yield","yieldAav")
pair$yieldAav=pair$yieldAav*10
pair$s_k=apply(pair[c(4,5)],c(1),sum,na.rm=t)/2
#pair$s_y=apply(pair[c(4,6)],c(1),sum,na.rm=t)/2
pair$s_k_y=apply(pair[c(4:6)],c(1),sum,na.rm=t)/3
pair$s_k_y_y=apply(pair[c(4:7)],c(1),sum,na.rm=t)/4


pair2=melt(pair, id.vars=c("spp","k1","k2"), measure.vars=c("safety","s_k","s_k_y","s_k_y_y"))
pair2$variable=as.character(pair2$variable)

pair2$variable[pair2$variable=="s_k"] = "safety/kobe"
pair2$variable[pair2$variable=="s_k_y"] = "safety/kobe/yield"
pair2$variable[pair2$variable=="s_k_y_y"] = "safety/kobe/yield/yieldvar"

te=ddply(na.omit(pair2),.(spp,variable),transform, var2=minMax(value))

te$variable = factor(te$variable, levels=c("safety","safety/kobe","safety/kobe/yield","safety/kobe/yield/yieldvar"))
te$spp = factor(te$spp, levels=c("ray","pollack","turbot","brill", "sprat"))

te<- te[!is.na(te$spp), ]
```
## utilities plots
```{r, utilplot, echo=TRUE, fig=TRUE}
ggplot(subset(te, !(spp %in% c("lobster", "razor")))) + 
  aes(x = k1, y = k2, z = var2, fill = var2) + 
  geom_tile() + 
  #coord_equal() +
  #geom_contour(color = "white", alpha = 0.5) + 
  #scale_fill_distiller("",palette="Spectral", na.value="white", direction=1) + 
  #geom_contour(color = "white", alpha = 0.1) + 
  scale_fill_gradientn("utility",colours=mycol, breaks=c(0, 0.5, 1))+
  geom_contour(color = "white", alpha = 0.3) + 
  #scale_fill_distiller("",palette="Spectral", na.value="white", direction=1, breaks=c(0, 0.5, 1))+
  theme_bw()+facet_grid(spp~variable) +
  theme(text = element_text(size=18, face="bold"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        legend.position="bottom",panel.spacing = unit(1, "lines")
        ) + ylab("k2")+xlab("k1")


#ggsave(filename='/Users/alextidd/Documents/fig6.png',last_plot(),dpi=300, units='in',width=12,height=14)
```

## Author information

**Alex Tidd**. emperorfish@gmail.com


## Acknowledgements

This vignette and many of the methods documented in it were developed under the MyDas project funded by the Irish exchequer and EMFF 2014-2020. The overall aim of MyDas is to develop and test a range of assessment models and methods to establish Maximum Sustainable Yield (MSY) reference points (or proxy MSY reference points) across the spectrum of data-limited stocks.
